---
title: "R Analysis Example"
author: "Your Name"
date: today
format:
  html:
    code-fold: show
    code-tools: true
---

## Introduction

This document demonstrates R-based statistical analysis for the thesis.

## Setup

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(ggplot2)
library(broom)
library(knitr)

# Set theme
theme_set(theme_minimal())
```

## Load Data

```{r}
# Generate sample data
set.seed(123)
n <- 200

df <- tibble(
  x = rnorm(n, mean = 50, sd = 10),
  y = 2 * x + rnorm(n, mean = 0, sd = 15),
  category = sample(c("A", "B", "C"), n, replace = TRUE)
)

head(df)
```

## Descriptive Statistics

```{r}
# Summary by category
df %>%
  group_by(category) %>%
  summarise(
    mean_x = mean(x),
    mean_y = mean(y),
    sd_x = sd(x),
    sd_y = sd(y),
    n = n()
  ) %>%
  kable(digits = 2, caption = "Summary Statistics by Category")
```

## Visualization

```{r}
#| label: fig-scatter
#| fig-cap: "Relationship between X and Y variables"
#| fig-width: 8
#| fig-height: 6

ggplot(df, aes(x = x, y = y, color = category)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1) +
  labs(
    title = "Scatter Plot with Linear Regression",
    x = "X Variable",
    y = "Y Variable",
    color = "Category"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme_minimal(base_size = 12)
```

## Statistical Modeling

```{r}
# Fit linear model
model <- lm(y ~ x + category, data = df)

# Model summary
summary(model)
```

```{r}
# Tidy model output
tidy(model) %>%
  kable(digits = 3, caption = "Model Coefficients")
```

```{r}
# Model diagnostics
glance(model) %>%
  kable(digits = 3, caption = "Model Fit Statistics")
```

## Residual Analysis

```{r}
#| label: fig-residuals
#| fig-cap: "Residual diagnostics"
#| fig-width: 10
#| fig-height: 8

par(mfrow = c(2, 2))
plot(model)
```

## Results

::: {.callout-tip}
## Model Performance
- R² = `r round(summary(model)$r.squared, 3)`
- Adjusted R² = `r round(summary(model)$adj.r.squared, 3)`
- The model shows a strong positive relationship between X and Y
:::

## Conclusion

The analysis reveals significant relationships in the data. Further investigation is needed to validate these findings with additional datasets.
